Interval Probability for Fuzzy Quantum Theories

### 2016-05-21 prob.tex
prob.tex Modify the discription of preposing symbols a little bit...

The conventional definition of a probability
space~\cite{Kolmogorov1950,Shafer1976,Griffiths2003,Swart2013}
builds upon the real numbers. In more detail, a probability space
consists of a \emph{sample space} $\Omega$, a space of
\emph{events}~$\events$, and a \emph{probability measure}~$\pmeas$
mapping events in $\events$ to the real interval $[0,1]$. In this
paper, we will only consider \emph{finite} sets of events: we
therefore restrict our attention to non-empty finite sets $\Omega$ as
the sample space. The space of events $\events$ includes every
possible subset of $\Omega$: it is the powerset~$2^\Omega$. Given the
set of events $\events$, a \emph{probability measure} is a function
$\pmeas : \events \rightarrow [0,1]$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = 1$, and 
\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$,
where $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}a_{i}$
explicitly specifies $a_{i}\in\mathbb{R}$. We may drop the preposing
$\mathbb{R}$ when there is no confusion. 
\end{itemize}

@@

As motivated above, an event $E_1$ may have an interval of probability
$[l_1,r_1]$. Assume that another disjoint event $E_2$ has interval
probability $[l_2,r_2]$, what is the interval probability of the event
$E_1 \cup E_2$? The answer is somewhat subtle: although it is possible
to use the sum of the intervals $[l_1+l_2,r_1+r_2]$ as the combined
probability, one can do find a much tighter interval if information
\emph{against} the event (i.e., information about the complement
event) is also taken into consideration. Formally, for a general event
$E$ with probability $[l,r]$, the evidence that
contradicts $E$ is an evidence supporting the complement of $E$. The
complement of $E$ must therefore have probability
$\left[1-r,1-l\right]$ which we abbreviate $1\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
where the preposing $\mathscr{I}$ specifies we subtracts intervals,
and may be dropped clearly by content. Given
a collection of intervals $\mathscr{I}$, an
$\mathscr{I}$--interval-valued probability measure is a function
$\pmeas : \events \rightarrow \mathscr{I}$ such that:
\begin{itemize}
\item $\pmeas(\emptyset)=[0,0]$, 
\item $\pmeas(\Omega)=[1,1]$, 
\item $\pmeas\left(\Omega\backslash E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\pmeas\left(E\right)$,
  and 
\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\pmeas\left(E_{i}\right)$,
where $\tensor*[_{\mathscr{I}}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i}}r_{i}\right]$.
We may drop the preposing $\mathscr{I}$ when summands are clearly intervals. 
\end{itemize}

@@

\begin{definition}[Projection Operators;
Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}.} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_1$ and $P_2$ are \emph{orthogonal} if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
is also a projection operator if and only if they are orthogonal, 
where the preposing subscript $\mathscr{O}$
means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators,
and may be dropped when there is no ambiguity. 
\item Conversely, every projection~$P$ can be expressed as
$\tensor*[_{\mathscr{O}}]{\sum}{_j}\proj{\psi_{j}}$,
where $P$ actually projects onto the linear subspace~$S$ which
has an orthonormal basis~$\{\ket{\psi_{j}}\}$. 
\end{itemize}
\qed\end{definition}

>>>>

The conventional definition of a probability
space~\cite{Kolmogorov1950,Shafer1976,Griffiths2003,Swart2013}
builds upon the real numbers. In more detail, a probability space
consists of a \emph{sample space} $\Omega$, a space of
\emph{events}~$\events$, and a \emph{probability measure}~$\pmeas$
mapping events in $\events$ to the real interval $[0,1]$. In this
paper, we will only consider \emph{finite} sets of events: we
therefore restrict our attention to non-empty finite sets $\Omega$ as
the sample space. The space of events $\events$ includes every
possible subset of $\Omega$: it is the powerset~$2^\Omega$. Given the
set of events $\events$, a \emph{probability measure} is a function
$\pmeas : \events \rightarrow [0,1]$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = 1$, and 
\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$,
where $\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\pmeas(E_{i})$
explicitly specifies $\pmeas(E_{i})\in\mathbb{R}$. Besides $\mathbb{R}$, We will
prepose other symbols later to specify the type of operations, and they may be
dropped when there is no ambiguity.
\end{itemize}

@@

As motivated above, an event $E_1$ may have an interval of probability
$[l_1,r_1]$. Assume that another disjoint event $E_2$ has interval
probability $[l_2,r_2]$, what is the interval probability of the event
$E_1 \cup E_2$? The answer is somewhat subtle: although it is possible
to use the sum of the intervals $[l_1+l_2,r_1+r_2]$ as the combined
probability, one can do find a much tighter interval if information
\emph{against} the event (i.e., information about the complement
event) is also taken into consideration. Formally, for a general event
$E$ with probability $[l,r]$, the evidence that
contradicts $E$ is an evidence supporting the complement of $E$. The
complement of $E$ must therefore have probability
$\left[1-r,1-l\right]$ which we abbreviate $1\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
where the preposing $\mathscr{I}$ specifies we subtracts intervals. Given
a collection of intervals $\mathscr{I}$, an
$\mathscr{I}$--interval-valued probability measure is a function
$\pmeas : \events \rightarrow \mathscr{I}$ such that:
\begin{itemize}
\item $\pmeas(\emptyset)=[0,0]$, 
\item $\pmeas(\Omega)=[1,1]$, 
\item $\pmeas\left(\Omega\backslash E\right)=1\tensor*[_{\mathscr{I}}]{-}{}\pmeas\left(E\right)$,
  and 
\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i}}\pmeas\left(E_{i}\right)$,
where $\tensor*[_{\mathscr{I}}]{\sum}{_{i}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i}}r_{i}\right]$.
We may drop the preposing $\mathscr{I}$ when summands are clearly intervals. 
\end{itemize}

@@

\begin{definition}[Projection Operators;
Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Griffiths2003,Swart2013}]
\label{def:Projection} Given a Hilbert space $\Hilb$, an event\footnote{An event
is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936}, a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}.} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection. 
\item For any pure state~$\ket{\psi}$, $\proj{\psi}$ is a projection
operator. 
\item Projection operators $P_1$ and $P_2$ are \emph{orthogonal} if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two projection operators~$P_{1}\tensor*[_{\mathscr{O}}]{+}{}P_{2}$
is also a projection operator if and only if they are orthogonal, 
where the preposing subscript $\mathscr{O}$
means $\tensor*[_{\mathscr{O}}]{+}{}$ is an operation between operators. 
\item Conversely, every projection~$P$ can be expressed as
$\tensor*[_{\mathscr{O}}]{\sum}{_j}\proj{\psi_{j}}$,
where $P$ actually projects onto the linear subspace~$S$ which
has an orthonormal basis~$\{\ket{\psi_{j}}\}$. 
\end{itemize}
\qed\end{definition}
